---
title: "Data Science for WASH - An opportunity for the sector"
description: |
  Workshop hosted at the Colorado WASH Symposium 2021 
author:
- name: Lars Schöbitz
  url: https://www.lse.de
  affiliation: Lars Schöbitz GmbH
  affiliation_url: https://www.lse.de
- name: Georges Mikhael
  url: https://www.linkedin.com/in/georges-mikhael-340996140/
  affiliation: Aguaconsult Ltd.
  affiliation_url: https://aguaconsult.co.uk/
  date: "`r Sys.Date()`"
site: distill::distill_website
---

<script async defer data-domain="larnsce.github.io/co-wash-symposium-2021" src="https://plausible.io/js/plausible.js"></script>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```


# 👋 Welcome

These are the materials and instructions for a workshop hosted on Day 2 of the [Colorado WASH Symposium 2021](https://www.colorado.edu/washsymposium/). 


```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

```{r embed-xaringan, echo=FALSE, fig.cap="[Slides](slides/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/index.html", ratio = "16:9")
```

# 📆 Details

- **Date:** Friday, 12th March 2021
- **Time:**
    - 7 AM (MST - Boulder, USA) `r emo::ji("us")`
    - 3 PM (CET - Zurich, Switzerland)  `r emo::ji("switzerland")`
    - 5 PM (EAT - Nairobi, Kenya) `r emo::ji("kenya")`
    - 9 PM (ICT - Hanoi, Vietnam) `r emo::ji("vietnam")`
    - 1 AM (NSW - Syndey, Australia) `r emo::ji("australia")` **"Sorry!"**
 
# ✏️ Prework

We assume that you have:

1. Registered for Colorado WASH Sympsoium 2021 ([register here](https://wash21.paperform.co/)) 
2. Created a free account on RStudio Cloud ([create one here](https://rstudio.cloud/plans/free))
3. Read the [Code of Conduct](https://larnsce.github.io/co-wash-symposium-2021/code_of_conduct.html) for this workshop

We do not expect any prior knowlegde of using R or RStudio.

# 🏁 Objectives

As part of the workshop you will:

- follow along an example to produce a data analysis report using data of the [WHO/UNICEF Joint Monitoring Programme for Water Supply and Sanitation](https://washdata.org/)
- learn how to use the [R Markdown](https://rmarkdown.rstudio.com/) document format to produce an HTML document, and how to publish it as a website
- get a taste of the benefits of using R as a modern data science tool for reproducible data analyses and reporting

# Acknowledgments {.appendix}

This is website made with the [distill package](https://rstudio.github.io/distill/) and is inspired by the layout of [Teaching in Production](https://rstudio-education.github.io/teaching-in-production/) by [Alison Hill](https://alison.rbind.io/).